Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-06-17 manuscripts/manuscript.Rmd
update refs

Each of the policy adjustment cost function is characterized in terms of
a cost coefficient $c_i$. However, $c_i$ takes different units for each
functional form. Therefore, if seeking to compare the relative effect of
each penalty function on optimal management, it is unclear what
parameter values should be used. To address this issue, we calibrate
choices of $c_i$ so that each has a comparable impact on the optimal net
present value of fishery, broadly following the example of Bovenberg,
Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).
<!--NOTE Jake to confirm these are still relevant and needed. We are using a less sophisticated normalization than was once discussed and may or may not need the citations now. -->

>>>>

Each of the policy adjustment cost function is characterized in terms of
a cost coefficient $c_i$. However, $c_i$ takes different units for each
functional form. Therefore, if seeking to compare the relative effect of
each penalty function on optimal management, it is unclear what
parameter values should be used. To address this issue, we calibrate
choices of $c_i$ so that each has a comparable impact on the optimal net
present value of fishery, broadly following the example of  @Bovenberg_2008.

<!--NOTE Jake to confirm these are still relevant and needed. We are using a less sophisticated normalization than was once discussed and may or may not need the citations now. -->
